Sweep Z - general experiment analysis.

### 2018-04-03 voltagebudget/analysis/sweep_Z_analysis.Rmd
Update Z vis Rmd

```{r, message=FALSE}
# Osc
freq <- "40"

# Zs scan
exp <- "74"
Zs <- c("0.1", "0.2", "0.3")

results <- NULL
for(Z in Zs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, "_Z", Z, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))

@@

# Ref (Z=0)
exp <- "72"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$Zs <- rep(0, nrow(df))
results <- rbind(df, results)

# Process
results %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) %>% 
  mutate(silent = n_spikes_ref == 0) -> results

@@

@@

>>>>

```{r, message=FALSE}
# Osc
freq <- "20"

# Zs scan
exp <- "98"
Zs <- c("0.1", "0.2", "0.3")

results <- NULL
for(Z in Zs){
  name <- paste("../data/exp", exp, "_Z", Z, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))

@@

# Ref (Z=0)
exp <- "96"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$Zs <- rep(0, nrow(df))
results <- rbind(df, results)

# Process
results %>% 
  filter(n_spikes_ref > 0) %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) %>% 
  mutate(silent = n_spikes_ref == 0) -> results

@@

# V_osc/V_b

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=V_osc/V_b, y=n_spikes_pop, color=factor(Zs))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### Errors

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors_pop, color=factor(Zs))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(errors < 0.1) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~Zs) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(errors < 0.1) %>%
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N, Zs) %>% 
  mutate(norm_errors = errors/max(errors)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~Zs) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### Variances

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances_pop, color=factor(Zs))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0, V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop, color=factor(Zs))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~Zs) +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom")
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~Zs) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

## Metrics

@@

## n_spikes v rest
